---
title: "ghypernet Tutorial"
author: "Giona Casiraghi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ghypernet Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r}
library(ghypernet)
data("adj_karate")
directed <- FALSE
selfloops <- FALSE
print(adj_karate[1:10,1:10])

(sprad <- eigen(adj_karate)$values[1])
```

```{r}
(regmodel <- regularm(graph = adj_karate, directed = directed, selfloops = selfloops))
print(regmodel$xi[1:10,1:10])

random_graphs <- rghype(nsamples = 100, model = regmodel)
spradii <- sapply(X = random_graphs, FUN = function(mat) eigen(mat + t(mat))$values[1] )
summary(spradii)
```

```{r}
(confmodel <- scm(graph = adj_karate, directed = directed, selfloops = selfloops))
print(confmodel$xi[1:10,1:10])

random_graphs <- rghype(nsamples = 100, model = confmodel)
spradii <- sapply(X = random_graphs, FUN = function(mat) eigen(mat + t(mat))$values[1] )
summary(spradii)
```

```{r}
data("vertexlabels")
(blockmodel <- bccm(adj = adj_karate, labels = vertexlabels, directed = directed, selfloops = selfloops))
print(blockmodel$blockOmega)

(blockmodel_2 <- bccm(adj = adj_karate, labels = vertexlabels, directed = directed, selfloops = selfloops, homophily = TRUE))
```

```{r}
conf.test(graph = adj_karate, directed = directed, selfloops = selfloops)
```

```{r}
lr.test(nullmodel = confmodel, altmodel = blockmodel)
lr.test(nullmodel = confmodel, altmodel = blockmodel_2)
lr.test(nullmodel = blockmodel_2, altmodel = blockmodel)
```

```{r}
AIC(regmodel)
AIC(confmodel)
AIC(blockmodel_2)
AIC(blockmodel)
```

```{r}
BIC(regmodel)
BIC(confmodel)
BIC(blockmodel_2)
BIC(blockmodel)
```

```{r}
fullmodel <- ghype(graph = adj_karate, directed = directed, selfloops = selfloops, unbiased = FALSE)

AIC(fullmodel)
BIC(fullmodel)

lr.test(nullmodel = blockmodel_2, altmodel = fullmodel, nempirical = 1000, seed = 123)
gof.test(model = blockmodel_2, nempirical = 1000, seed = 123)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
