---
title: "Finding Significant Links with Hypernets"
author: "Giona CasiraghI"
date: "20/4/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this example we use the hypernets package to detect significant links.
We use the Karate Club as running example.

### Load Packages

```{r}
library(hypernets)
library(igraph)
library(igraphdata)
data("karate")
```

### Estimate the ensemble

First we estimate a soft-configuration model from the data.
The second model is a block model based on the two 'factions' of members of the club

```{r}
adj <- get.adjacency(karate, attr = 'weight', sparse = F)

mod <- scm(adj,directed = F, selfloops = F)

blockModel <- bccm(adj = adj, labels = V(karate)$Faction, directed = F, selfloops = F, homophily = T)
```

## Finding the significance of the links
We use the built-in function in the hypernets package to compute the significance of each link as described in Casiraghi et al. 2017.
The function takes the adjacency matrix of the network and the model from which estimating the probability to observe as many edges as those in the graph.
We can obtain a high-pass noise filtering choosing a significance level and filtering those links which have a low significance.

```{r}
# obtain significance matrix
signmat <- linkSignificance(adj, mod)

# filter adjacency matrix
adjfiltered <- adj
adjfiltered[signmat<(1/mod$m)] <- 0
```

### Plot the results

We plot the original graph first, then a graph were the non-significant links are colored red.
The final plot only shows the significant links.

Note that the configuration model is not able to predict the strong links within the groups, as those go beyond simple degree effects.
The results reflect this showing the two factions separated and only the links due to homophily effect left.

```{r}
adjcolor <- adj
adjcolor[adj>0] <- 2
adjcolor[signmat<(1/mod$m)] <- 1
diag(adjcolor) <- 0
gfiltered <- graph_from_adjacency_matrix(adjfiltered, mode = 'upper')
g <-  graph_from_adjacency_matrix(adjcolor, mode = 'upper', weighted = 'color')
E(g)$color[E(g)$color==1] <- "red"
E(g)$color[E(g)$color==2] <- "black"

V(gfiltered)$color <- V(g)$color <- V(karate)$color
plot(karate)
plot(g)
plot(gfiltered)
```


## Block Model
As the Karate Club consists of two factions, we can refine the model adding the block structure to it.
Then we can filter out the links that are not significant according to this more complex model.

What we expect in this case is that most of the whithin-group links are now not significant anymore, as they can be explained by the joint effect of configuration model and block model.
Hence the links that remains after filtering are those that go beyond this joint effect.
In particular, only few nodes of a group interact with the other group, i.e. the between-groups links are concentrated between few dyads.
From the model instead we should expect most nodes of a group weakly interacting with the other group.
Hence, we can expect that the significant links will be mainly those between groups.
The results are in accordance with our intuition.

```{r}
signmat <- linkSignificance(adj, blockModel)
adjfiltered <- adj
adjfiltered[signmat<(1/mod$m)] <- 0
```

```{r}
adjcolor <- adj
adjcolor[adj>0] <- 2
adjcolor[signmat<(1/mod$m)] <- 1
diag(adjcolor) <- 0
gfiltered <- graph_from_adjacency_matrix(adjfiltered, mode = 'upper')
g <-  graph_from_adjacency_matrix(adjcolor, mode = 'upper', weighted = 'color')
E(g)$color[E(g)$color==1] <- "red"
E(g)$color[E(g)$color==2] <- "black"

V(gfiltered)$color <- V(g)$color <- V(karate)$color
plot(karate)
plot(g)
plot(gfiltered)
```
